%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{enumitem}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sunidhi Mundra} \\ \vspace{1pt}
    \href{tel:+918319712343}{\underline{+91 8319712343}} $|$ \href{mailto:sunidhi.m.work@gmail.com}{\underline{sunidhi.m.work@gmail.com}} $|$ 
    \href{www.linkedin.com/in/sunidhi-mundra}{\underline{Linkedin}} $|$
    \href{https://github.com/foundsunidhi}{\underline{Github}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology(VIT) }{Bhopal, IN}
      {Integrated Master of Technology in Artificial Intelligence}{September 2024 -- 2029}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Software Development Engineer (SDE) Intern}{March 2024 -- Present}
      {Viskk}{Remote}
      \resumeItemListStart
       \resumeItem{Developing a Windows application focused on enhancing user productivity and screen management.}
        \resumeItem{Optimizing application performance and functionality to ensure a smooth user experience.}
        \resumeItem{Collaborating with the team to refine the software and enhance its practical usability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{TicketScanning App} $|$ \emph{Flutter, MongoDB, QR Code Scanner}}{October 2024}
          \resumeItemListStart
            \resumeItem{Developed a ticket validation system for seamless event check-ins.}
            \resumeItem{Implemented QR code scanning with real-time ticket status updates (Invalid, Checked-in, Already Checked-in).}
            \resumeItem{Integrated MongoDB as the backend for storing and validating ticket information.}
            \resumeItem{Built a user-friendly UI in Flutter to ensure smooth scanning and error handling.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Leaderboard} $|$ \emph{Next.js, Google Sheets API}}{Feb 2025}
          \resumeItemListStart
            \resumeItem{Built a leaderboard system that dynamically fetches data from Google Sheets.}
            \resumeItem{Designed a responsive UI that displays rankings for multiple categories.}
            \resumeItem{Implemented a seamless data retrieval mechanism without requiring a dedicated backend.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI-Based Language Translator} $|$ \emph{Next.js, Google Translate API}}{March 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Creating a real-time translation app using Next.js and Google Translate API.}
            \resumeItem{Designing a modular architecture to support multiple languages efficiently.}
            \resumeItem{Optimizing UI for fast translations and smooth user experience.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Dart} \\
     \textbf{Frameworks}{: Flutter} \\
     \textbf{APIs}{: Google Sheets API, Google Translate API} \\
     \textbf{Tools and Platforms}{: Git, Google Cloud Console}
    }}
 \end{itemize}

%-----------ACTIVITIES-----------
%-----------ACTIVITIES-----------
\section{Activities}
    \resumeItemListStart
        \resumeItem{Active member of the Fintech Club at VIT(Bhopal). Member of the Technical Team, contributing to the development and optimization of digital solutions to enhance club initiatives and operations.}
    \resumeItemListEnd
\end{document}
